%!TEX root = ../cv_bruno.tex

\begin{rSection}{Supervision}

\begin{rSubsection}{PhD Students}{}{}{}

\item Alex Rutherford  (w/ N. Hawes \&  J. Foerster) \hfill September 2022 -- Present\\
\textit{Topic: Multi-Agent Reinforcement Learning for Multi-Robot Coordination}

\item Carl Hentges  (w/ N. Hawes \& D. Parker) \hfill September 2022 -- Present\\
\textit{Topic: Formal Methods for Planning with Uncertain Models}

\item Michal Staniaszek  (w/ N. Hawes) \hfill September 2022 -- Present\\
\textit{Topic: Long-Term Robot Inspection in Nuclear Environments}

\item Alex Stephens  (w/ N. Hawes) \hfill September 2021 -- Present\\
\textit{Topic: Planing for Long-Term Science Missions}

\item Matthew Budd  (w/ N. Hawes \& P. Duckworth) \hfill September 2020 -- Present\\
\textit{Topic: Integrating MDP Planning with Gaussian Process Prediction}

\item Clarissa Costen  (w/ N. Hawes) \hfill September 2020 -- Present\\
\textit{Topic: Shared Autonomy with Formal Guarantees}

\item Mohamed Baioumy  (w/ N. Hawes \& P. Duckworth) \hfill September 2019 -- Present\\
\textit{Topic: Variational Inference for Decision Making under Uncertainty}

\item Anna Gautier (w/ N. Hawes \& M. Wooldridge) \hfill September 2019 -- Present\\
\textit{Topic: Noncooperative Multi-Robot Systems}

\item  Charlie Street (w/ Nick Hawes) \hfill September 2018 -- September 2022\\
\textit{Topic: AI for Multi-Robot Systems}

\item  Marc Rigter (w/ Nick Hawes) \hfill September 2018 -- Present\\
\textit{Topic: Planning with Learned Models}

\item  Michael Painter  (w/ Nick Hawes) \hfill September 2018 -- Present\\
\textit{Topic: Multi-Objective Mission Planning}

\item  Fatma Faruq  (w/ David Parker and Nick Hawes) \hfill February 2017 -- August 2021\\
\textit{Topic: Simultaneous Task Allocation and Planning under Uncertainty}

\item  Lenka Mudrova (w/ Nick Hawes) \hfill June 2014 -- September 2017\\
\textit{Topic: Task Scheduling and Merging in Space and Time}

\end{rSubsection}

\begin{rSubsection}{Final Year Projects}{}{}{}

\item Alex Rutherford  \hfill October 2021 -- May 2022\\
\textit{4th Year Project. Topic: Multi-Agent Reinforcement Learning}

\item Yifeng Wei  \hfill October 2020 -- May 2021\\
\textit{4th Year Project. Topic: Trial-based Search for Generalised Stochastic Petri Nets}

\item Matthew Budd  (w/ Paul Duckworth)  \hfill October 2019 -- May 2020\\
\textit{4th Year Project. Topic: Safe Exploration of MDPs with Gaussian Processes}

\item Han Zhou \hfill October 2018 -- May 2019\\
\textit{4th Year Project. Topic: Auctioning for Multi-Robot Coordination}

\item   Milan Tomy (w/ Jeremy Wyatt)\hfill June 2017 -- September 2017\\
\textit{MSc Summer Project. Topic: Battery Scheduling in Autonomous Mobile Robots}

\item   Joseph Shaw (w/ Nick Hawes) \hfill October 2016 -- April 2017\\
\textit{BSc Final Year Project. Topic: Auctioning for Multi-Robot Coordination}

\item  Pedro Elias (w/ Nick Hawes)  \hfill June 2015 -- September 2015\\
\textit{MSc Summer Project. Topic: Multi-agent Path Finding}

\item  Eliot Dixon  (w/ Nick Hawes) \hfill June 2014 -- September 2014\\
\textit{MSc Summer Project. Topic: MDP Models for Mobile Service Robots}

\item  Ken Poyner (w/ Nick Hawes) \hfill June 	2013 -- September 2013\\
\textit{MSc Summer Project. Topic: Autonomous Navigation Cost Estimation In Mobile Robots}

\end{rSubsection}

\end{rSection}
